### 2017-03-31 manuscript/publication-si-recipe.tex
tweaks

In the Organic Potatoes example presented in the text, the product system was characterized with respect to six different LCIA methods, all representing different implementations of the ReCiPe Marine Eutrophication midpoint indicator, measured in kg N-equivalents.  Ecoinvent's LCIA implementation is available by request from the Ecoinvent Centre; it has not changed since 2014. The ReCiPe method has been implemented according to the Individualist (I), Hierarchist (H), and Egalitarian (E) modes specified in the methodology; in addition, the (I) and (H) methods have been reimplemented in a way that omits long-term emissions.  The European Life Cycle Database's reference implementation of marine eutrophication was last updated in 2011.  The dataset cites the 2008 version of ReCiPe.

The tabular output of the structured publication provides a convenient method to compare the implementations. Inspection reveals that, as far as marine eutrophication  is concerned, there is no difference among the (I), (H), and (E) modes, which all have the same characterization factors.  Similarly, the (I) and (H) methods omitting long-term emissions are also the same.  Both sets of Ecoinvent indicators bear similarities and differences to the ILCD implementation, however.  The differences are shown in Table~\ref{table:recipe}.

>>>>

In the Organic Potatoes example presented in the text, the product system was characterized with respect to six different LCIA methods, all representing different implementations of the ReCiPe Marine Eutrophication midpoint indicator, measured in kg N-equivalents.  Ecoinvent's LCIA implementation is available by request from the Ecoinvent Centre; it has not changed since 2014. The ReCiPe method has been implemented according to the Individualist (I), Hierarchist (H), and Egalitarian (E) modes specified in the methodology; in addition, the (E) and (H) methods have been reimplemented in a way that omits long-term emissions.  The European Life Cycle Database's reference implementation of marine eutrophication was last updated in 2011.  The dataset cites the 2008 version of ReCiPe.

The tabular output of the structured publication provides a convenient method to compare the implementations. Inspection reveals that, as far as marine eutrophication  is concerned, there is no difference among the (I), (H), and (E) modes, which all have the same characterization factors.  Similarly, the (E) and (H) methods omitting long-term emissions are also the same.  Both sets of Ecoinvent indicators bear similarities and differences to the ILCD implementation, however.  The differences are shown in Table~\ref{table:recipe}.
